The Concurrent Calculi Formalisation Benchmark

### 2024-02-22 short-paper/short-paper.tex
fix in intro about Kohei 09 paper

In this spirit, we introduce a new collection of benchmark problems
specifically crafted to tackle common challenges encountered during
the mechanisation of formal models for concurrent and distributed
programming languages.
We particularly focus on process calculi as these provide a simple but
realistic showcase of common issues encountered during mechanisation
efforts.
Concurrent calculi are notably subtle: for instance, it took nine
years before the incorrect proof of type safety in the seminal paper
by Honda et al.~\cite{Honda1998} was rectified in Yoshida and
Vasconcelos’s subsequent work\cite{Yoshida2007}.\todo{Marco: rewrite this to be correct}
Similarly, several key results in papers on session types have turned out
to be false later on~\cite{Gay2020,10.1145/3290343}, illustrating the
value of machine-checked proofs.\todo{Rephrase this sentence to be more clear on the references}

>>>>

In this spirit, we introduce a new collection of benchmark problems
specifically crafted to tackle common challenges encountered during
the mechanisation of formal models for concurrent and distributed
programming languages.  We particularly focus on process calculi as
these provide a simple but realistic showcase of common issues
encountered during mechanisation efforts.  Concurrent calculi are
notably subtle: for instance, it took some years before the incorrect
subject reduction proof in the original paper on session
subtyping~\cite{GH99} was rectified in the journal extended
version~\cite{GH05} with the use of polarities. % , and generally
% addressed by Vasconcelos and Yoshida~\cite{Yoshida2007}.
% it took nine years before the incorrect proof of type safety in the
% seminal paper by Honda et al.~\cite{Honda1998} was rectified in
% Yoshida and Vasconcelos’s subsequent
% work\cite{Yoshida2007}.\todo{Marco: rewrite this to be correct}
Similarly, other key results in session types papers have subsequently
been proven incorrect~\cite{Gay2020,10.1145/3290343}, advocating the
need for machine-checked proofs.
% \todo{Rephrase this sentence to be more clear on the references}
